The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-05-06 paper.tex
work on the observations description now

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{figures/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO LWA.
        The 200 meter diameter area indicated by the dashed line contains 251 antennas distributed
        in a pseudo-random configuration. The 32 filled circles are the expansion antennas built in
        early 2016 to increase the longest baseline to 1.5 km. The 5 open circles are antennas
        equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO LWA is a low-frequency
instrument with instantaneous bandwidth covering 24.768 MHz to 82.296 MHz \todo{double check this
frequency range, I think it's wrong}.  Each antenna stand hosts two perpendicular broadband dipoles
so that there are $288\times2$ signal paths in total. These signal paths feed into the 512-input
LEDA correlator, which allows the OVRO LWA to capture the entire visible hemisphere in a single
snapshot image.  In the current configuration, 32 antennas (64 signal paths) are unused.

The 288 antennas are arranged in a maximally non-redundant configuration optimized for minimum
sidelobes in snapshot imaging. 251 of these antennas are contained within a 200 m diameter core that
is independently optimized for imaging sidelobe levels. 32 antennas are placed outside of the core
in order to extend the maximum baseline length out to $\sim$1.5 km. The final 5 antennas are
equipped with noise-switched front ends for calibrated total power measurements of the global sky
brightness. These antennas are used as part of the LEDA experiment to measure the global signal of
21 cm absorption from the cosmic dawn. \todo{cite a leda paper} Calibrated total power measurements
from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.
\todo{What values of $l$ actually contribute to the total power measurements?}

%See Figure~\ref{fig:antenna-layout} for an image of the antenna
%layout. The antennas can be categorized into 3 groups:
%\begin{enumerate}
%    \item
%        Core antennas - 251 antennas are contained within a 200 m diameter core where they are
%        arranged in a configuration optimized to reduce sidelobe levels in snapshot imaging.
%    \item
%        Total power antennas - 5 antennas are equipped with noise-switched front ends for calibrated
%        total power measurements of the sky brightness.
%    \item
%        Expansion antennas - 32 additional antennas were installed in early 2016. These antennas
%        extend the longest baselines of the OVRO LWA out to 1.5 km. This allows for $\sim10$
%        arcminute resolution in the snapshot images.
%\end{enumerate}
%When fully completed, the OVRO LWA will have 352 antennas in total spanning 2.5 km.
%
%\todo{cite Gregg's instrument paper}
%
%The field-of-view and compactness of the OVRO LWA make it a promising instrument for 21 cm
%cosmology. The field-of-view increases the number of cosmological modes measured at any instant in
%time. The inner core of 251 antennas within a 200 m diameter provides excellent brightness
%temperature sensitivity. Figure~\ref{fig:ps-sensitivity} shows the expected signal-noise ratio
%achieved by the OVRO LWA on the three-dimensional spatial power spectrum of 21 cm emission for a
%variety of models. A large integration time and careful calibration will be needed to make a
%detection.
%
%The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-antenna interferometer located at the
%Owens Valley Radio Observatory (OVRO) near Big Pine, California. Each antenna is composed of two
%crossed dipoles bringing the total number of signal paths to 576.  The OVRO LWA hosts the LEDA
%correlator that allows cross-correlation of 512 signal paths with $>50$ MHz instantaneous bandwidth.
%
%Of the 288 antennas, 251 are located within a 200 m diameter core.  The location of these antennas
%has been optimized to minimize imaging sidelobes.  5 antenna stands are dedicated to the LEDA
%experiment and have switching front-ends for total-power radiometry. The remaining 32 antennas
%extend out to 2 km baselines to improve the angular resolution of the interferometer.

\subsection{The OVRO LWA 100 Hour Dataset}

Because the correlator only accepts 512 inputs (256 antennas with 2 polarizations for each antenna),
a subset of the antennas must be selected for correlation.

Include plot of antenna layout.

The integration time is 13 seconds. This was chosen because the remainder of one sidereal day
divided into 13 second intervals is only 90 milliseconds.  Finer control of the integration time is
not possible due to technical constraints.

\subsection{Antenna Gain Calibration}

@@

@@

\subsection{Fitting the Antenna Response}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{figures/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

The Owens Valley Long Wavelength Array (OVRO LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory (OVRO) near Big Pine, California.  The OVRO LWA is a low-frequency
instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz and 24 kHz channelization.
Each antenna stand hosts two perpendicular broadband dipoles so that there are $288\times2$ signal
paths in total. These signal paths feed into the 512-input LEDA correlator
\citep{2015JAI.....450003K}, which allows the OVRO LWA to capture the entire visible hemisphere in a
single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
of the global sky brightness.  These antennas are used as part of the LEDA experiment \todo{cite
Price et al. 2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.

\todo{cite Gregg's instrument paper}

Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
environment considerably. During this time the OVRO LWA operated as a zenith-pointing drift scanning
interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
output evenly divides a sidereal day.

\todo{describe the ionospheric conditions at the time}

\subsection{Gain Calibration}

@@

\subsection{Primary Beam Measurements}

@@
